---
title: "Team 8: Credit Chronicles "
author: "Members: Sai Krishna ,Gourab Mukherjee, Tulasi"
#date: "`r Sys.Date()`"
output:
  html_document:
    css: custom_theme.css
    code_folding: hide
---


```{r init, include=F}
# The package "ezids" (EZ Intro to Data Science) includes some helper functions we developed for the course. 
# Some of the frequently used functions are loadPkg(), xkabledply(), xkablesummary(), uzscale(), etc.
# You will need to install it (once) from GitHub.
#install.packages("devtools")
#library(devtools)
#devtools::install_github("physicsland/ezids")
# Then load the package in your R session.
library(ezids)
```


```{r setup, include=FALSE}
# Some of common RMD options (and the defaults) are: 
# include=T, eval=T, echo=T, results='hide'/'asis'/'markup',..., collapse=F, warning=T, message=T, error=T, cache=T, fig.width=6, fig.height=4, fig.dim=c(6,4) #inches, fig.align='left'/'center','right', 
knitr::opts_chunk$set(warning = F, message = F)
# Can globally set option for number display format.
options(scientific=T, digits = 3) 
# options(scipen=9, digits = 3) 
```
<h1 style="color: RED;"><b>DATA PREPROCESSING</b></h1>
<h1 style="color: white;"><b>LOADING DATASET & CHECKING str():</b></h1>
```{r reading_datafile_credit_card_churn.csv  , include=TRUE}
library(readr)
credit_card <- read.csv("credit_card.csv")
print(str(credit_card))


```
<h1 style="color: white;"><b>DIMENSIONS OF DATA: </b></h1>
```{r}
dim(credit_card)
```
<h1 style="color: white;"><b>SUMMARY OF DATASET:</b></h1>
```{r}
summary(credit_card)
```
<h1 style="color: white;"><b>COLUMN NAMES IN THE DATASET:</b></h1>
```{r Column_names , include=TRUE}
column_names <- colnames(credit_card)
last_two_columns <- tail(column_names, 2)
print(column_names)

```
<h1 style="color: white;"><b>DATA TYPES OF COLUMNS:</b></h1>
```{r Data_Types_of_Columns, include=TRUE}
column_data_types <- sapply(credit_card, class)
print(column_data_types)
```
<h1 style="color: white;"><b>AFTER DROPING UNNECESSARY COLUMNS:</b></h1>
```{r Dropping_last_two_columns_to_get_final_dataframe , include=TRUE}

credit_card_final <- subset(credit_card,select = !colnames(credit_card) %in% last_two_columns)
print(colnames(credit_card_final))

```
<h1 style="color: white;"><b>CHECKING FOR NULL VALUES</b></h1>
```{r}
null_counts <- colSums(is.na(credit_card_final))
print(null_counts)
```

<h1 style="color: white;"><b>REPLACING SPACES WITH NA AND CHECKING FOR NULL VALUES OR UNFILLED VALUES </b></h1>
```{r}
credit_card_final[credit_card_final == " "] <- NA
null_counts1 <- colSums(is.na(credit_card_final))
print(null_counts1)
```
<h1 style="color: white;"><b>CATEGORICAL VARIABLES:</b></h1>
```{r Categorical_Variables, include=TRUE}
library(dplyr)

# Identify categorical variables (regardless of data type)
categorical_variables <- credit_card_final %>%
  select_if(function(col) is.character(col) || is.factor(col)) %>%
  names()

print(categorical_variables)
```
<h1 style="color: white;"><b>NUMERICAL VARIABLES:</b></h1>
```{r Numerical_Variables, include=TRUE}
library(dplyr)

# Identify numerical variables (excluding character and factor)
numerical_variables <- credit_card_final %>%
  select_if(function(col) is.numeric(col)) %>%
  names()

# Separate continuous and discrete variables
continuous_variables <- credit_card_final %>%
  select(numerical_variables) %>%
  summarise_all(function(col) isTRUE(all.equal(col, round(col))))

discrete_variables <- setdiff(numerical_variables, continuous_variables)

# Combine continuous and discrete variables into a single output
variables_summary <- list(Continuous = continuous_variables, Discrete = discrete_variables)

# Print the variables summary
print(discrete_variables)
print(continuous_variables)
```

<h1 style="color: RED;"><b>EDA --> "Exploratory Data Analysis"</b></h1>

<h1 style="color: white;"><b>DATA DISTRIBUTION OF CATEGORICAL VARIABLES:</b></h1>
```{r Data Distribution , include=TRUE}
library(ggplot2)

categorical_vars_ggplot <- c("Attrition_Flag", "Gender", "Education_Level", "Marital_Status", "Income_Category", "Card_Category")

for (cat_var in categorical_vars_ggplot) {
  plot_obj <- ggplot(credit_card_final, aes_string(x = cat_var, fill = cat_var)) + 
    geom_bar() +
    geom_text(stat='count', aes_string(label='..count..', y='..count..'), vjust=-0.5) +
    labs(title = paste("Distribution of", cat_var), x = cat_var, y = "Count") +
    scale_fill_brewer(palette="Set3") + 
    theme_minimal() +  
    theme(legend.position="none")  
  
  print(plot_obj)
}

```
```{r}
# Load necessary libraries
library(ggplot2)

# Create a bar graph
ggplot(credit_card_final, aes(x = Card_Category, y = Credit_Limit, fill = Card_Category)) +
  geom_bar(stat = "identity") +
  labs(title = "Credit Limit by Card Category",
       x = "Card Category",
       y = "Credit Limit") +
  theme_minimal()

```
```{r}
# Load necessary libraries
#library(ggplot2)

# Create a bar graph with facets
#ggplot(credit_card_final, aes(x = Gender, y = Avg_Utilization_Ratio, fill = Gender)) +
 # geom_bar(stat = "identity") +
  #labs(title = "Avg Utilization Ratio and Avg Open To Buy by Gender",
    #   x = "Gender",
   #    y = "Avg Utilization Ratio") +
  #facet_wrap(~ Avg_Open_To_Buy, ncol = 3) +
  #theme_minimal()

```



<h1 style="color: white;"><b>CUSTOMER SEGMENTATION:</b></h1>
```{r Customer Segmentation, include=TRUE}
# Load necessary libraries
library(dplyr)
library(ggplot2)

# Select relevant attributes for segmentation
selected_attributes <- credit_card_final %>% 
  select(Customer_Age, Income_Category, Card_Category)

# Define the segmentation criteria (you can adjust these criteria as needed)
young_high_income <- with(credit_card_final, Customer_Age < 35 & Income_Category >= 4)
middle_age_high_income <- with(credit_card_final, Customer_Age >= 35 & Customer_Age <= 60 & Income_Category >= 4)
senior_high_income <- with(credit_card_final, Customer_Age > 60 & Income_Category >= 4)
young_low_income <- with(credit_card_final, Customer_Age < 35 & Income_Category < 4)
middle_age_low_income <- with(credit_card_final, Customer_Age >= 35 & Customer_Age <= 60 & Income_Category < 4)
senior_low_income <- with(credit_card_final, Customer_Age > 60 & Income_Category < 4)

# Assign segments to the original dataset
credit_card_final$Segment <- ifelse(young_high_income, "Young High Income",
                          ifelse(middle_age_high_income, "Middle Age High Income",
                          ifelse(senior_high_income, "Senior High Income",
                          ifelse(young_low_income, "Young Low Income",
                          ifelse(middle_age_low_income, "Middle Age Low Income",
                          ifelse(senior_low_income, "Senior Low Income", NA))))))

# Visualize the segmentation
ggplot(credit_card_final, aes(x = Customer_Age, y = Income_Category, color = Segment)) +
  geom_point() +
  labs(title = "Customer Segmentation by Age and Income Category")

# Summary statistics for each segment
segment_summary <- credit_card_final %>%
  group_by(Segment) %>%
  summarise(
    Average_Age = mean(Customer_Age),
    Average_Income = mean(Income_Category)
  )
print(segment_summary)

```

```{r Card Segmentation, include=TRUE}
# Segment customers based on Card Category
credit_card_final$Card_Segment <- ifelse(credit_card_final$Card_Category == "Blue", "Blue Card",
                        ifelse(credit_card_final$Card_Category == "Silver", "Silver Card",
                        ifelse(credit_card_final$Card_Category == "Gold", "Gold Card",
                        ifelse(credit_card_final$Card_Category == "Platinum", "Platinum Card", NA))))

# Visualize the Card Category segmentation
ggplot(credit_card_final, aes(x = Customer_Age, y = Income_Category, color = Card_Segment)) +
  geom_point() +
  labs(title = "Customer Segmentation by Age and Income Category (Card Category)")

# Summary statistics for each Card Category segment
card_category_summary <- credit_card_final %>%
  group_by(Card_Segment) %>%
  summarise(
    Average_Age = mean(Customer_Age),
    Average_Income = mean(Income_Category)
  )
print(card_category_summary)

```


<h1 style="color: white;"><b>DATA DISTRIBUTION OF NUMERICAL VARIABLES:</b></h1>
```{r Data_Distribution, include=TRUE}
library(ggplot2)

# Define a list of column names and corresponding bin widths
column_binwidths <- list(
  "Customer_Age" = 3,
  "Total_Trans_Amt" = 500,
  "Total_Trans_Ct" = 7,
  "Credit_Limit" = 800
)

# Loop through the columns and create histograms with respective bin widths and density curves
for (column in names(column_binwidths)) {
  # Get the bin width for the current column
  binwidth <- column_binwidths[[column]]
  
  # Create a histogram with density curve
  hist_plot <- ggplot(credit_card_final, aes(x = .data[[column]])) +
    geom_histogram(binwidth = binwidth, fill = "pink", color = "black", aes(y = ..density..)) +
    geom_density(alpha = 0.5, color = "green") +
    labs(title = paste("Histogram with Density Curve of", column)) +
    theme_minimal()
  
  # Display the histogram with density curve
  print(hist_plot)
}

```

<h1 style="color: white;"><b>CORRELATION ANALYSIS:</b></h1>
```{r Correlation_Analysis, include=TRUE}
#install.packages("corrplot")
library(corrplot)

# Calculate the correlation matrix for numerical variables
correlation_matrix <- cor(credit_card_final[, numerical_variables])

# Create a correlation plot
corrplot(correlation_matrix, method = "color", type = "upper", tl.col = "black", tl.srt = 50)

# Display the correlation plot
```
```{r}
# Calculate the correlation matrix
correlation_matrix <- cor(credit_card_final[, numerical_variables])

# Find highly correlated pairs
threshold <- 0.7  # Set your desired correlation threshold

# Create an empty matrix to store the results
related_pairs <- matrix(nrow = 0, ncol = 2)

# Loop through the correlation matrix to find related pairs
for (i in 1:(length(numerical_variables) - 1)) {
  for (j in (i + 1):length(numerical_variables)) {
    if (abs(correlation_matrix[i, j]) >= threshold) {
      related_pairs <- rbind(related_pairs, c(numerical_variables[i], numerical_variables[j]))
    }
  }
}

# Display related variable pairs
print(related_pairs)

```

<h1 style="color: white;"><b>CORRELATION COEFFICIENTS:</b></h1>
```{r Correlation Coefficients, include=TRUE}
# Define the pairs of variables
variable_pairs <- list(
  c("Customer_Age", "Months_on_book"),
  c("Credit_Limit", "Avg_Open_To_Buy"),
  c("Total_Trans_Amt", "Total_Trans_Ct")
)

# Function to calculate and display correlation
calculate_and_display_correlation <- function(pair) {
  variable1 <- pair[1]
  variable2 <- pair[2]
  
  # Extract data for the pair
  data_pair <- credit_card_final[, c(variable1, variable2)]
  
  # Calculate correlation
  correlation_coefficient <- cor(data_pair[[variable1]], data_pair[[variable2]])
  
  # Print the correlation result
  cat("Correlation between", variable1, "and", variable2, "is", correlation_coefficient, "\n")
}

# Loop through variable pairs and calculate/display correlations
for (pair in variable_pairs) {
  calculate_and_display_correlation(pair)
}

```

<h1 style="color: white;"><b>PLOTTING THE PAIRS:</b></h1>
```{r Scatter Plot, include=TRUE}
# Load necessary libraries
library(ggplot2)

# List of related variable pairs
related_pairs <- list(
  list("Customer_Age", "Months_on_book"),
  list("Credit_Limit", "Avg_Open_To_Buy"),
  list("Total_Trans_Amt", "Total_Trans_Ct")
)

# Create a function to plot scatter plots with regression lines for a pair of related variables
plot_scatter_with_regression <- function(pair) {
  # Extract variable names
  var1 <- pair[[1]]
  var2 <- pair[[2]]
  
  # Create a scatter plot
  scatter_plot <- ggplot(credit_card_final, aes(x = .data[[var1]], y = .data[[var2]])) +
    geom_point(alpha = 0.6, size = 3, color = "orchid") +
    geom_smooth(method = "lm", se = FALSE, color = "dodgerblue", size = 1) +
    labs(
      title = paste("Scatter Plot of", var1, "vs", var2),
      x = var1,
      y = var2
    ) +
    theme_minimal()
  
  # Set the size of the plot
  options(repr.plot.width = 6, repr.plot.height = 4)
  
  # Display the scatter plot with a regression line
  print(scatter_plot)
}

# Loop through related variable pairs and create individual scatter plots
for (pair in related_pairs) {
  plot_scatter_with_regression(pair)
}

```
```{r Creating Histograms and QQplots, include=TRUE}
# Load necessary libraries
library(ggplot2)
library(gridExtra)

# Define the pairs of variables
variable_pairs <- list(
  c("Customer_Age", "Months_on_book"),
  c("Credit_Limit", "Avg_Open_To_Buy"),
  c("Total_Trans_Amt", "Total_Trans_Ct")
)

# Create a function to plot histograms and QQ-plots for a variable pair
plot_histogram_qqpair <- function(pair) {
  variable1 <- pair[1]
  variable2 <- pair[2]
  
  # Extract data for the pair
  data_pair <- credit_card_final[, c(variable1, variable2)]
  
  # Create a histogram for variable 1
  hist_var1 <- ggplot(data_pair, aes(x = .data[[variable1]])) +
    geom_histogram(binwidth = 10, color = "black", fill = "darkgoldenrod") +
    labs(title = paste("Histogram of", variable1)) +
    theme_minimal()
  
  # Create a histogram for variable 2
  hist_var2 <- ggplot(data_pair, aes(x = .data[[variable2]])) +
    geom_histogram(binwidth = 10, color = "black", fill = "tomato") +
    labs(title = paste("Histogram of", variable2)) +
    theme_minimal()
  
  # Create a QQ-plot
  qqplot <- ggplot(data_pair, aes(sample = .data[[variable1]])) +
    geom_qq() +
    geom_qq_line(color = "darkolivegreen") +
    labs(title = paste("QQ-Plot of", variable1, "vs Normal Distribution")) +
    theme_minimal()
  
  # Arrange histograms and QQ-plot in one grid
  grid.arrange(hist_var1, hist_var2, qqplot, ncol = 2)
}

# Loop through variable pairs and plot histograms and QQ-plots
for (pair in variable_pairs) {
  plot_histogram_qqpair(pair)
}

```

<h1 style="color: white;"><b> OUTLIER DETECTION AND REMOVAL:</b></h1>
```{r Outlier Dectection, include=TRUE}
# Create a copy of the dataset to avoid modifying the original data
credit_card_no_outliers <- credit_card_final
# Outlier Identifiaction and removal from Customer Age
  df_outliers <- ezids::outlierKD2(credit_card_no_outliers,Customer_Age, rm = TRUE, boxplt = TRUE, qqplt = TRUE)
  credit_card_no_outliers[["Customer_Age"]][df_outliers$outliers] <- NA

  # Outlier Identifiaction and removal from Credit Limit
  df_outliers <- ezids::outlierKD2(credit_card_no_outliers,Credit_Limit, rm = TRUE, boxplt = TRUE, qqplt = TRUE)
  credit_card_no_outliers[["Credit_Limit"]][df_outliers$outliers] <- NA
  
# Outlier Identifiaction and removal from Months on Book
  df_outliers <- ezids::outlierKD2(credit_card_no_outliers,Months_on_book, rm = TRUE, boxplt = TRUE, qqplt = TRUE)
  credit_card_no_outliers[["Months_on_book"]][df_outliers$outliers] <- NA
  
# Outlier Identifiaction and removal from Total Revolving Balance
  df_outliers <- ezids::outlierKD2(credit_card_no_outliers,Total_Revolving_Bal, rm = TRUE, boxplt = TRUE, qqplt = TRUE)
  credit_card_no_outliers[["Total_Revolving_Bal"]][df_outliers$outliers] <- NA
  
# Outlier Identifiaction and removal from Total Transaction Amount 
  df_outliers <- ezids::outlierKD2(credit_card_no_outliers,Total_Trans_Amt, rm = TRUE, boxplt = TRUE, qqplt = TRUE)
  credit_card_no_outliers[["Total_Trans_Amt"]][df_outliers$outliers] <- NA
  
# Outlier Identifiaction and removal from Total Transaction Ct
  df_outliers <- ezids::outlierKD2(credit_card_no_outliers,Total_Trans_Ct, rm = TRUE, boxplt = TRUE, qqplt = TRUE)
  credit_card_no_outliers[["Total_Trans_Ct"]][df_outliers$outliers] <- NA

# Outlier Identifiaction and removal from Average Open to Buy
  df_outliers <- ezids::outlierKD2(credit_card_no_outliers,Avg_Open_To_Buy, rm = TRUE, boxplt = TRUE, qqplt = TRUE)
  credit_card_no_outliers[["Avg_Open_To_Buy"]][df_outliers$outliers] <- NA
  
# Outlier Identifiaction and removal from Average Utilization Ratio
  df_outliers <- ezids::outlierKD2(credit_card_no_outliers,Avg_Utilization_Ratio, rm = TRUE, boxplt = TRUE, qqplt = TRUE)
  credit_card_no_outliers[["Avg_Utilization_Ratio"]][df_outliers$outliers] <- NA

```

```{r checking_graph after removed_Outlier, include=TRUE}

library(ggplot2)
library(gridExtra)

# Define the pairs of variables
variable_pairs <- list(
  c("Customer_Age", "Months_on_book"),
  c("Credit_Limit", "Avg_Open_To_Buy"),
  c("Total_Trans_Amt", "Total_Trans_Ct")
)

# Create a function to plot histograms and QQ-plots for a variable pair
plot_histogram_qqpair <- function(pair) {
  variable1 <- pair[1]
  variable2 <- pair[2]
  
  # Extract data for the pair
  data_pair <- credit_card_no_outliers[, c(variable1, variable2)]
  
  # Create a histogram for variable 1
  hist_var1 <- ggplot(data_pair, aes(x = .data[[variable1]])) +
    geom_histogram(binwidth = 10, color = "black", fill = "darkgoldenrod") +
    labs(title = paste("Histogram of", variable1)) +
    theme_minimal()
  
  # Create a histogram for variable 2
  hist_var2 <- ggplot(data_pair, aes(x = .data[[variable2]])) +
    geom_histogram(binwidth = 10, color = "black", fill = "tomato") +
    labs(title = paste("Histogram of", variable2)) +
    theme_minimal()
  
  # Create a QQ-plot
  qqplot <- ggplot(data_pair, aes(sample = .data[[variable1]])) +
    geom_qq() +
    geom_qq_line(color = "darkolivegreen") +
    labs(title = paste("QQ-Plot of", variable1, "vs Normal Distribution")) +
    theme_minimal()
  
  # Arrange histograms and QQ-plot in one grid
  grid.arrange(hist_var1, hist_var2, qqplot, ncol = 2)
}

# Loop through variable pairs and plot histograms and QQ-plots
for (pair in variable_pairs) {
  plot_histogram_qqpair(pair)
}

```

```{r checking SD, include=TRUE }
# Calculate the standard deviation for each specified column
std_dev_Customer_Age <- sd(credit_card_no_outliers$Customer_Age)
std_dev_Credit_Limit <- sd(credit_card_no_outliers$Credit_Limit)
std_dev_Months_on_book <- sd(credit_card_no_outliers$Months_on_book)
std_dev_Avg_Open_To_Buy <- sd(credit_card_no_outliers$Avg_Open_To_Buy)
std_dev_Avg_Utilization_Ratio <- sd(credit_card_no_outliers$Avg_Utilization_Ratio)
std_dev_Total_Revolving_Bal <- sd(credit_card_no_outliers$Total_Revolving_Bal)
std_dev_Total_Trans_Amt <- sd(credit_card_no_outliers$Total_Trans_Amt)
std_dev_Total_Trans_Ct <- sd(credit_card_no_outliers$Total_Trans_Ct)

# Create a data frame with column names and standard deviations
std_dev_table <- data.frame(
  Column = c("Customer_Age", "Credit_Limit", "Months_on_book", "Avg_Open_To_Buy",
             "Avg_Utilization_Ratio", "Total_Revolving_Bal", "Total_Trans_Amt", "Total_Trans_Ct"),
  Standard_Deviation = c(std_dev_Customer_Age, std_dev_Credit_Limit, std_dev_Months_on_book, std_dev_Avg_Open_To_Buy,
                         std_dev_Avg_Utilization_Ratio, std_dev_Total_Revolving_Bal, std_dev_Total_Trans_Amt, std_dev_Total_Trans_Ct)
)

# Load the knitr package
library(knitr)

# Print the table using knitr
print(std_dev_table, align = "c", col.names = c("Column", "Standard Deviation"), caption = "Standard Deviations")


```



```{r}
# Perform t-test
t_test_result <- t.test(credit_card_no_outliers$Total_Trans_Amt ~ credit_card_no_outliers$Gender)

# Print the results
print("T-test for Total_Trans_Amt and Gender")
print(t_test_result)
```



```{r}
# Create a contingency table of income category and churn status
table_data <- table(credit_card_no_outliers$Income_Category, credit_card_no_outliers$Income_Category)

# Perform chi-square test
chi_sq_test <- t.test(table_data)

# Print the test results
chi_sq_test
```


```{r}
# Plot 1
ggplot(credit_card_final, aes(x=Credit_Limit, y=Avg_Utilization_Ratio)) +
  geom_point(alpha=0.5, colour='blue', shape=4) +
  ggtitle("Example Plot") +
  xlab("Credit Limit") +
  ylab("Average Utilization Ratio") +
  theme_minimal()

# Plot 2
ggplot(credit_card_final[credit_card_final$Income_Category != "Unknown", ], 
       aes(x = Customer_Age, y = Credit_Limit, color = Income_Category)) +
  geom_point(alpha = 0.6) +
  ggtitle("Relation Between Credit Limit Vs Age Coloured by Income_Category") +
  xlab("Age") +
  ylab("Credit Limit") +
  scale_colour_viridis_d() +
  theme_minimal() +
  theme(legend.position = "right")


```




```{r}

# Perform t-test for Contacts_Count_12_mon between attrition and non-attrition groups
attrition_group <- credit_card_final$Contacts_Count_12_mon[credit_card_final$Attrition_Flag == "Attrited Customer"]
non_attrition_group <- credit_card_final$Contacts_Count_12_mon[credit_card_final$Attrition_Flag == "Existing Customer"]

t_test_result <- t.test(attrition_group, non_attrition_group)

# Print t-test results
print(t_test_result)
```

```{r}
contingency_table_income <- table(credit_card_no_outliers$Income_Category , credit_card_no_outliers$Attrition_Flag)

ChiS2_test_income <- chisq.test(contingency_table_income)
print(contingency_table_income)
print(ChiS2_test_income)

Attrition_rate <- (contingency_table_income[,"Attrited Customer"]/ (contingency_table_income[,"Attrited Customer"]+contingency_table_income[,"Existing Customer"]))*100
print(Attrition_rate)

```

```{r}
# load libraries
library(dplyr)
library(ggplot2)

# group data
grouped_df <- credit_card_no_outliers %>%
               group_by(Income_Category) %>%
               summarise(Transaction_mean = mean(Total_Trans_Amt, na.rm = TRUE),
                         Transaction_median = median(Total_Trans_Amt, na.rm = TRUE),
                         n = n())

# plotting
ggplot(grouped_df, aes(x=Income_Category)) +
  geom_col(aes(y=Transaction_mean, fill="Mean"), width=0.4, position=position_dodge(width=0.5)) +
  geom_col(aes(y=Transaction_median, fill="Median"), width=0.4, position=position_dodge(width=0.5)) +
  labs(fill='Transaction', y='Transaction Value', title='Transaction Behaviour by Income Category') +
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, hjust=1))

```




```{r}
male_utilization <- credit_card_no_outliers[credit_card_no_outliers$Gender=="F",]$Avg_Utilization_Ratio
female_utilization <- credit_card_no_outliers[credit_card_no_outliers$Gender=="M",]$Avg_Utilization_Ratio

tt_result <- t.test(male_utilization, female_utilization)

print(tt_result)
```