---
title: "Team 8: Credit Chronicles "
author: "Members: Sai Krishna ,Gourab Mukherjee, Tulasi"
#date: "`r Sys.Date()`"
output:
  html_document:
    css: custom_theme.css
    code_folding: hide
---


```{r init, include=F}
# The package "ezids" (EZ Intro to Data Science) includes some helper functions we developed for the course. 
# Some of the frequently used functions are loadPkg(), xkabledply(), xkablesummary(), uzscale(), etc.
# You will need to install it (once) from GitHub.
#install.packages("devtools")
#library(devtools)
#devtools::install_github("physicsland/ezids")
# Then load the package in your R session.
library(ezids)
```


```{r setup, include=FALSE}
# Some of common RMD options (and the defaults) are: 
# include=T, eval=T, echo=T, results='hide'/'asis'/'markup',..., collapse=F, warning=T, message=T, error=T, cache=T, fig.width=6, fig.height=4, fig.dim=c(6,4) #inches, fig.align='left'/'center','right', 
knitr::opts_chunk$set(warning = F, message = F)
# Can globally set option for number display format.
options(scientific=T, digits = 3) 
# options(scipen=9, digits = 3) 
```
<h1 style="color: RED;"><b>DATA PREPROCESSING</b></h1>
<h1 style="color: white;"><b>LOADING DATASET & CHECKING str():</b></h1>
```{r reading_datafile_credit_card_churn.csv  , include=TRUE}
library(readr)
credit_card <- read.csv("credit_card.csv")
print(str(credit_card))


```
<h1 style="color: white;"><b>DIMENSIONS OF DATA: </b></h1>
```{r}
dim(credit_card)
```
<h1 style="color: white;"><b>SUMMARY OF DATASET:</b></h1>
```{r}
summary(credit_card)
```
<h1 style="color: white;"><b>COLUMN NAMES IN THE DATASET:</b></h1>
```{r Column_names , include=TRUE}
column_names <- colnames(credit_card)
last_two_columns <- tail(column_names, 2)
print(column_names)

```
<h1 style="color: white;"><b>DATA TYPES OF COLUMNS:</b></h1>
```{r Data_Types_of_Columns, include=TRUE}
column_data_types <- sapply(credit_card, class)
print(column_data_types)
```
<h1 style="color: white;"><b>AFTER DROPING UNNECESSARY COLUMNS:</b></h1>
```{r Dropping_last_two_columns_to_get_final_dataframe , include=TRUE}

credit_card_final <- subset(credit_card,select = !colnames(credit_card) %in% last_two_columns)
print(colnames(credit_card_final))

```
<h1 style="color: white;"><b>CHECKING FOR NULL VALUES</b></h1>
```{r}
null_counts <- colSums(is.na(credit_card_final))
print(null_counts)
```

<h1 style="color: white;"><b>REPLACING SPACES WITH NA AND CHECKING FOR NULL VALUES OR UNFILLED VALUES </b></h1>
```{r}
credit_card_final[credit_card_final == " "] <- NA
null_counts1 <- colSums(is.na(credit_card_final))
print(null_counts1)
```
<h1 style="color: white;"><b>CATEGORICAL VARIABLES:</b></h1>
```{r Categorical_Variables, include=TRUE}
library(dplyr)

# Identify categorical variables (regardless of data type)
categorical_variables <- credit_card_final %>%
  select_if(function(col) is.character(col) || is.factor(col)) %>%
  names()

print(categorical_variables)
```
<h1 style="color: white;"><b>NUMERICAL VARIABLES:</b></h1>
```{r Numerical_Variables, include=TRUE}
library(dplyr)

# Identify numerical variables (excluding character and factor)
numerical_variables <- credit_card_final %>%
  select_if(function(col) is.numeric(col)) %>%
  names()

# Separate continuous and discrete variables
continuous_variables <- credit_card_final %>%
  select(numerical_variables) %>%
  summarise_all(function(col) isTRUE(all.equal(col, round(col))))

discrete_variables <- setdiff(numerical_variables, continuous_variables)

# Combine continuous and discrete variables into a single output
variables_summary <- list(Continuous = continuous_variables, Discrete = discrete_variables)

# Print the variables summary
print(discrete_variables)
print(continuous_variables)
```
<h1 style="color: RED;"><b>EDA --> "Exploratory Data Analysis"</b></h1>

<h1 style="color: white;"><b>DATA DISTRIBUTION OF CATEGORICAL VARIABLES:</b></h1>
```{r Data Distribution , include=TRUE}
library(ggplot2)

categorical_vars_ggplot <- c("Attrition_Flag", "Gender", "Education_Level", "Marital_Status", "Income_Category", "Card_Category")

for (cat_var in categorical_vars_ggplot) {
  plot_obj <- ggplot(credit_card_final, aes_string(x = cat_var, fill = cat_var)) + 
    geom_bar() +
    geom_text(stat='count', aes_string(label='..count..', y='..count..'), vjust=-0.5) +
    labs(title = paste("Distribution of", cat_var), x = cat_var, y = "Count") +
    scale_fill_brewer(palette="Set3") + 
    theme_minimal() +  
    theme(legend.position="none")  
  
  print(plot_obj)
}

```
```{r}
# Load necessary libraries
library(ggplot2)

# Create a bar graph
ggplot(credit_card_final, aes(x = Card_Category, y = Credit_Limit, fill = Card_Category)) +
  geom_bar(stat = "identity") +
  labs(title = "Credit Limit by Card Category",
       x = "Card Category",
       y = "Credit Limit") +
  theme_minimal()

```
```{r}
# Load necessary libraries
library(ggplot2)

# Create a bar graph with facets
ggplot(credit_card_final, aes(x = Gender, y = Avg_Utilization_Ratio, fill = Gender)) +
 geom_bar(stat = "identity") +
  labs(title = "Avg Utilization Ratio and Avg Open To Buy by Gender",
       x = "Gender",
       y = "Avg Utilization Ratio") +
  facet_wrap(~ Avg_Open_To_Buy, ncol = 3) +
  theme_minimal()

```

<h1 style="color: white;"><b>CUSTOMER SEGMENTATION:</b></h1>
```{r Customer Segmentation, include=TRUE}
# Load necessary libraries
library(dplyr)
library(ggplot2)

# Select relevant attributes for segmentation
selected_attributes <- credit_card_final %>% 
  select(Customer_Age, Income_Category, Card_Category)

# Define the segmentation criteria (you can adjust these criteria as needed)
young_high_income <- with(credit_card_final, Customer_Age < 35 & Income_Category >= 4)
middle_age_high_income <- with(credit_card_final, Customer_Age >= 35 & Customer_Age <= 60 & Income_Category >= 4)
senior_high_income <- with(credit_card_final, Customer_Age > 60 & Income_Category >= 4)
young_low_income <- with(credit_card_final, Customer_Age < 35 & Income_Category < 4)
middle_age_low_income <- with(credit_card_final, Customer_Age >= 35 & Customer_Age <= 60 & Income_Category < 4)
senior_low_income <- with(credit_card_final, Customer_Age > 60 & Income_Category < 4)

# Assign segments to the original dataset
credit_card_final$Segment <- ifelse(young_high_income, "Young High Income",
                          ifelse(middle_age_high_income, "Middle Age High Income",
                          ifelse(senior_high_income, "Senior High Income",
                          ifelse(young_low_income, "Young Low Income",
                          ifelse(middle_age_low_income, "Middle Age Low Income",
                          ifelse(senior_low_income, "Senior Low Income", NA))))))

# Visualize the segmentation
ggplot(credit_card_final, aes(x = Customer_Age, y = Income_Category, color = Segment)) +
  geom_point() +
  labs(title = "Customer Segmentation by Age and Income Category")

# Summary statistics for each segment
segment_summary <- credit_card_final %>%
  group_by(Segment) %>%
  summarise(
    Average_Age = mean(Customer_Age),
    Average_Income = mean(Income_Category)
  )
print(segment_summary)

```
```{r Card Segmentation, include=TRUE}
# Segment customers based on Card Category
credit_card_final$Card_Segment <- ifelse(credit_card_final$Card_Category == "Blue", "Blue Card",
                        ifelse(credit_card_final$Card_Category == "Silver", "Silver Card",
                        ifelse(credit_card_final$Card_Category == "Gold", "Gold Card",
                        ifelse(credit_card_final$Card_Category == "Platinum", "Platinum Card", NA))))

# Visualize the Card Category segmentation
ggplot(credit_card_final, aes(x = Customer_Age, y = Income_Category, color = Card_Segment)) +
  geom_point() +
  labs(title = "Customer Segmentation by Age and Income Category (Card Category)")

# Summary statistics for each Card Category segment
card_category_summary <- credit_card_final %>%
  group_by(Card_Segment) %>%
  summarise(
    Average_Age = mean(Customer_Age),
    Average_Income = mean(Income_Category)
  )
print(card_category_summary)

```




<h1 style="color: white;"><b>DATA DISTRIBUTION OF NUMERICAL VARIABLES:</b></h1>
```{r Data_Distribution, include=TRUE}
library(ggplot2)

# Define a list of column names and corresponding bin widths
column_binwidths <- list(
  "Customer_Age" = 3,
  "Total_Trans_Amt" = 500,
  "Total_Trans_Ct" = 7,
  "Credit_Limit" = 800
)

# Loop through the columns and create histograms with respective bin widths and density curves
for (column in names(column_binwidths)) {
  # Get the bin width for the current column
  binwidth <- column_binwidths[[column]]
  
  # Create a histogram with density curve
  hist_plot <- ggplot(credit_card_final, aes(x = .data[[column]])) +
    geom_histogram(binwidth = binwidth, fill = "pink", color = "black", aes(y = ..density..)) +
    geom_density(alpha = 0.5, color = "green") +
    labs(title = paste("Histogram with Density Curve of", column)) +
    theme_minimal()
  
  # Display the histogram with density curve
  print(hist_plot)
}

```

<h1 style="color: white;"><b>CORRELATION ANALYSIS:</b></h1>
```{r Correlation_Analysis, include=TRUE}
#install.packages("corrplot")
library(corrplot)

# Calculate the correlation matrix for numerical variables
correlation_matrix <- cor(credit_card_final[, numerical_variables])

# Create a correlation plot
corrplot(correlation_matrix, method = "color", type = "upper", tl.col = "black", tl.srt = 50)

# Display the correlation plot
```
```{r}
# Calculate the correlation matrix
correlation_matrix <- cor(credit_card_final[, numerical_variables])

# Find highly correlated pairs
threshold <- 0.7  # Set your desired correlation threshold

# Create an empty matrix to store the results
related_pairs <- matrix(nrow = 0, ncol = 2)


